---
title: "CUNY    SPS    DATA607    Assignment 1"
author: "Tage N Singh"
date: "`r Sys.Date()`"
output: html_document
---
\n

### ASSIGNMENT OVERVIEW

#### The article pertaining to this dataset is shown below - Congress's Age Problem ( 1947 - 2013)
#### It provides a statistical perspective of a New York Times article published in April 2014
#### The main theme of the article is that the members of congress are considerably older than the constituents they represent

#### We will present some preliminary statistical analysis

##### Please use the link below to view the full article

#### https://fivethirtyeight.com/features/both-republicans-and-democrats-have-an-age-problem/

```{r,dataimport}

# Importing the data from Github

congress <- read.csv(file = 'https://raw.githubusercontent.com/tagensingh/SPS-DATA607-ASSIGNMENT-1/main/congress-terms.csv')

#summary(congress)
head(congress)

```
```{r,column-select,message = FALSE,warning = FALSE}

library(datasets)
library(ggplot2)
library(dplyr)
library("tidyverse")

# Confirming the data frame 
class(congress)

# Creating a subset of the original data with selected columns

congress2 <- congress [c(1,2,4,6,9,10,13)]

# Cleaning up the headers

names(congress2)[1] <- "Congress_No"
names(congress2)[2] <- "Chamber"
names(congress2)[3] <- "First_Name"
names(congress2)[4] <- "Last_Name"
names(congress2)[5] <- "State"
names(congress2)[6] <- "Party"
names(congress2)[7] <- "Age"

head(congress2)

#summary(congress2)

```

```{r,congress_age,message = FALSE,warning = FALSE}

congress_age <- congress2[c("Congress_No","Age")]%>% group_by(Congress_No)

head(congress_age)

#class(congress_age)

congress_meanage <-aggregate(x = congress_age$Age,                # Specify data column
                    by = list(congress_age$Congress_No),              # Specify group indicator
                    FUN = mean)


```

```{r,graphical representation}

colnames(congress_meanage)

names(congress_meanage)[1] <- "Congress_No"
names(congress_meanage)[2] <- "Average_Age"

head(congress_meanage)

ggplot(congress_meanage, aes(x=Congress_No, y= Average_Age )) +
  geom_line()

```

\n
### Conclusion/Observation

#### For the period studied (1947-2013), the average age of congress people generally increased
#### Except for the period 1994 to 1998 when the average age decreased

